\chaptera{Список литературы}

\begin{itemize}
\bibl{Mono} \textit{Ерусалимский Я.М.} Графы с нестандартной достижимостью: задачи, приложения /Я.М. Ерусалимский, В.А. Скороходов, М.В. Кузьминова, А.Г. Петросян~--- Ростов н/Д.: Южный федеральный университет, 2009. - 195 с.

\bibl{J} \textit{Жилякова Л.Ю.} Ресурсные сети и анализ их динамики ~--- М.: ИПУ РАН, 2013. - 305 с.

\bibl{Hasse} \textit{Хассе Г.} Лекции по теории чисел.~--- М.: Изд-во иностранной литературы, 1953. - 527 с.

\bibl{Cir} \textit{Johnson D.B.} Finding All the Elementary Circuits of a Directed Graph // SIAM J. Comput. – 1975. — Vol. 4., no.~1. — P. 77-84.

\bibl{Par} \textit{Lu W., Zhao Q., Zhou C.} A Parallel Algorithm for Finding All Elementary Circuits of a Directed Graph // Proceedings of the 37th Chinese Control Conference (Wuhan, China, 25-27 July 2018) — P. 3156-3161.

\bibl{BFS} \textit{Moore E.F.} The shortest path through a maze // Proceedings of an International Symposium on the Theory of Switching (Cambridge, Massachusetts, 2–5 April 1957) — Harvard University Press, 1959. — Vol. 2. — P. 285–292. — 345 p.

\bibl{Tar} \textit{Tarjan R. E.} Depth-first search and linear graph algorithms // SIAM J. Comput. – 1972. — Vol. 1., no. 2. — P. 146–160. 

\bibl{Par2} \textit{Fleischer L., Hendrickson B., Pinar A.} On Identifying Strongly Connected Components in Parallel // Proceedings of the 15 IPDPS 2000 Workshops on Parallel and Distributed Processing (London, UK, 1-5 May 2000) — P. 505–511.

\end{itemize}

